### 2018-02-22 paper/algorithm.tex

We have several participants: Alfred, Beth, Cathy and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

\subsection{File-sharing protocol}

>>>>

We consider several participants: Alfred, Beth, Cathy and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
  \David\}\)), hereafter called their device swarm.
Our system is composted of two network overlays: one protocol is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, our file-sharing protocol uses the local and global 
knowledges to coordinate file sharing between devices in different swarms.

@@

\subsection{File-sharing protocol}
\label{FileSharingProtocol}

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alfred when he shares a file from his laptop L with Beth.}
\end{figure}
